This paper is written as the final step into achieving my Bachelor of Science
in Applied Computer Science. For a period of 4 months I became part of Skyline's fast growing, innovative team.
Skyline Communications is active in many different domains within IT. It was therefore not difficult to obtain
a research subject. The core of their activities however is rather complex. Although the first chapter is mainly informative, I highly recommend you read it carefully.

I would like to take this opportunity to thoroughly thank those who supported me along the way. I believe this thesis has been significantly improved by their contributions. First of all I would like to thank my external promoter, Mr. P. Vancompernolle. In a short time lapse he was able to offer a challenging but appealing internship. I am extremely grateful.
During the course of my internship he was very eloquent, approachable and he supported me whenever needed.

I would like to thank Mr. K. Sys for his guidance. Not only during my internship but also during the last few years.
You have set an example of excellence as a mentor, instructor and role model. I wish to thank my developers squad, I could always depend on them for support and answers and a laugh in between.

I would like to show my gratitude to my significant other, Astrid, I was amazed by her willingness to proof read countless pages of meaningless tech jargon.
Finally, I would like to thank my amazing family for the support and constant encouragement they gave me.

Enjoy reading!

Emiel Van Severen

