\newglossaryentry{dma}
{
    name=DMA,
    description={DataMiner Agent is a single server in a DataMiner System, which has the ability to manage a certain number of devices and systems}
}

\newglossaryentry{dms}
{
    name=DMS,
    description={DataMiner System represents all the connected devices and systems within DataMiner}
}

\newglossaryentry{oss}
{
    name=OSS,
    description={Operations Support System is a computer system used in telecommunications service providers to manage their networks. It enables the service providers to monitor, control, analyse
    and manage the services on their network}
}

\newglossaryentry{kpi}
{
    name=KPI,
    description={Key Performance Indicator is a way of measuring a company's progress towards the goal it is trying to achieve}
}

\newglossaryentry{nms}
{
    name        = NMS,
    description = {Network Management System is a computer system designed for monitoring, maintaining and optimizing a network}
}
\newglossaryentry{hfc}{
    name        = HFC,
    description = {Hybrid Fibre-Coaxial is a term used by the telecommunications industry. A broadband network that combines optical fiber and coaxial cable to create broadband connections}
}

\newglossaryentry{wmi}{
    name        = WMI,
    description = {Windows Management Instrumentation is a set of specifications from Microsoft consolidating the management of devices and applications in a network of Windows computing systems. Meanwhile a new version has arisen called Windows Management Infrastructure (MI)}
}

\newglossaryentry{xml}{
    name        = XML,
    description = {e{X}tensible Markup Language is a markup language that defines a set of rules for encoding documents in a format that is both human-readable and machine-readable}
}

\newglossaryentry{bis}{
    name        = BIS,
    description = {Business Intelligence Software is a type of software created to retrieve, analyse, visualize and report data. The BIS is often used as support in making a wide range of business decisions},
}
\newglossaryentry{ui}{
    name        = UI,
    description = {User Interface is the point of human-computer interaction and communication in a device. This can include display screens, keyboards, a mouse and the appearance of a desktop. It is also the way through which a user interacts with an application or a website \cite{m-rouse}}
}
\newglossaryentry{viewport}{
    name        = viewport,
    description = {The viewport is the user's visible area of a web page. Depending on the device, this will vary. A mobile phone's viewport will be smaller than a computer screen's viewport}
}

\newglossaryentry{sql}{
    name        = SQL,
    description = Structured Query Language is a standardized programming language to manage and manipulate relational databases. 
}