\chapter{Comparing prototyping software}

\section{Introduction}
Before you create prototypes it is important to understand who your users are and what issues they have. I have worked out user personas, use cases and more for Skyline Communications' customers..You can find these in \autoref{app:skyline-communication}.

\section{Prototyping software}
The prototyping software business has become a very competitive market, particularly in the last 5 to 10 years. Every company needs/wants a website. Chances are that your local bakery and butchery have one. Although these software tools are rapidly improving and adding new features persistently, until now they are still mostly limited to the visual design.

What is the best tool for creating large tables and the functionalities that go with that? Do the current software tools support these features or where are they lacking? Below you can find the tools that are being compared:
\begin{itemize}
    \setlength\itemsep{-0.5em}                                    
    \item {Adobe XD}
    \item {Figma}
    \item {Invision Studio}
    \item {Framer}
    \item {Axure RP}
    \item {Sketch}
\end{itemize}

Mind you, Sketch had been adopted as the industry standard for years. But excellent competitions changed this. Currently Its market position is being jeopardized. Although Sketch has been immensely popular, it forces you to use macOS. Since I do not own a device with macOS, it can not be tested properly. Sketch is too big of a player to leave out. The results of Sketch are discussed less extensively, without hands on testing. 

\section{Properties and features}
To compare the tools, I have carefully selected criteria. this includes both general criteria and criteria specifically required to visualize large tabular data. Below are the criteria that will be discussed in \autoref{chap:research-criteria}:  

    \begin{itemize}
    \setlength\itemsep{-0.5em}    
        \item{Popularity}
        \item{Price}
        \item{Platform}
        \item{Collaboration}
        \item{Sharing}
        \item{Community}
        \item{Handoffs}
        \item{Horizontal scroll bar}
        \item{Click events}
        \item{View lock}
        \item{Context menu}
    \end{itemize}